Accurate binding of sodium and calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-12-12 Manuscript/manuscript.tex
Added reference for MDAnalysis, cited VMD.

\begin{figure}[tb!]
  \centering
  \includegraphics[width=8.0cm]{../Fig/isocontours_r37_ca_O-carb.png} %\\
%  \includegraphics[width=8.0cm]{../Fig/volmap_resid10_Ca_Cl_PO4Cent.png} %\\
%  \includegraphics[width=4.0cm]{../Fig/volmap_resid10_Ca_Cl_sn1Cent.png}
%  \includegraphics[width=3.6cm]{../Fig/volmap_resid10_Ca_Cl_sn2Cent.png}
  \caption{\label{fig:volmaps}
      Isocontours of spatial number density of \ce{Ca^{2+}} (cyan, 0.0015~\AA$^{-3}$) 
      and POPC carbonyl oxygen atoms (red, 0.0075~\AA$^{-3}$, all POPC lipids contribute). 
      Calcium cations localize mostly around phosphate oxygens (red and bronze).
      Interactions with carbonyl oxygens is less likely than with phosphate oxygens, 
      and it is contributed more by other neighbouring phospholipids than by the same lipid. 
      Transparent structures are shown to depict the variability of POPC configurations. 
      The number density was evaluated for each lipid, 
      after its strucutral alignment using only phosphate group. 
      Carbon atoms are cyan, hydrogen atoms white, oxygen atoms red, nitrogen blue.
      %moiety, side chain 1 carbonyl group and side chain 2 carbonyl group.
      %Shown contours suggest that the dominant contribution 
      %to \ce{Ca^{2+}} binding comes from the phosphate oxygens,
      %whereas the interactions with any of the two carbonyl groups are considerably milder.
  }
  %\todo{The figure should be updated as discussed last week. Joe: Will only smoothen the isosurfaces now. }
\end{figure}

@@

This work can be reached as a repository containing all data at \url{zenodo.org:\dots\dots\dots}.

>>>>

\begin{figure}[tb!]
  \centering
  \includegraphics[width=8.0cm]{../Fig/isocontours_r37_ca_O-carb.png} %\\
%  \includegraphics[width=8.0cm]{../Fig/volmap_resid10_Ca_Cl_PO4Cent.png} %\\
%  \includegraphics[width=4.0cm]{../Fig/volmap_resid10_Ca_Cl_sn1Cent.png}
%  \includegraphics[width=3.6cm]{../Fig/volmap_resid10_Ca_Cl_sn2Cent.png}
  \caption{\label{fig:volmaps}
      Isocontours of spatial number density of \ce{Ca^{2+}} (cyan, 0.0015~\AA$^{-3}$) 
      and POPC carbonyl oxygen atoms (red, 0.0075~\AA$^{-3}$, all POPC lipids contribute). 
      Calcium cations localize mostly around phosphate oxygens (red and bronze).
      Interactions with carbonyl oxygens is less likely than with phosphate oxygens, 
      and it is contributed more by other neighbouring phospholipids than by the same lipid. 
      Transparent structures are shown to depict the variability of POPC configurations. 
      The number density was evaluated for each lipid, 
      after its strucutral alignment using only phosphate group. 
      MDAnalysis \cite{mdanalysis2011} library was used for 
      the calculations of the structural alignment and the spatial number density. 
      VMD \cite{hump96} was used for visualisation. 
      Carbon atoms are cyan, hydrogen atoms white, oxygen atoms red, nitrogen blue.
      %moiety, side chain 1 carbonyl group and side chain 2 carbonyl group.
      %Shown contours suggest that the dominant contribution 
      %to \ce{Ca^{2+}} binding comes from the phosphate oxygens,
      %whereas the interactions with any of the two carbonyl groups are considerably milder.
  }
  %\todo{The figure should be updated as discussed last week. Joe: Will only smoothen the isosurfaces now. }
\end{figure}

@@

This work can be reached as a repository containing all data and scripts for analysis at \url{zenodo.org:\dots\dots\dots}.
